Dynamical modeling of tidal streams

### 2013-09-30 tex/ms.tex
stream: some plots of the stream
streams: action-angle structure of simulation

>>>>

\begin{figure}[t!]
  \includegraphics[width=0.5\textwidth,clip=]{gd1_evol_xz.ps}
  \caption{}\label{fig:gd1_xy}
%python plot_stream.py ../tex/gd1_evol_xz.ps
\end{figure}

\begin{figure}[t!]
  \includegraphics[width=\textwidth,clip=]{gd1_evol_lb.ps}
  \includegraphics[width=\textwidth,clip=]{gd1_evol_ld.ps}
  \caption{}\label{fig:gd1_xy}
%python plot_stream.py ../tex/gd1_evol_lb.ps
%python plot_stream.py ../tex/gd1_evol_ld.ps
\end{figure}

\begin{figure}[t!]
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_aajrjz.ps}
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_aaoroz.ps}
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_aaaraz.ps}\\
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_aajrjp.ps}
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_aaorop.ps}
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_aaarap.ps}
  \caption{}\label{fig:gd1_xy}
%python plot_stream.py ../tex/gd1_evol_aajrjz.ps
%python plot_stream.py ../tex/gd1_evol_aaoroz.ps
%python plot_stream.py ../tex/gd1_evol_aaaraz.ps
%python plot_stream.py ../tex/gd1_evol_aajrjp.ps
%python plot_stream.py ../tex/gd1_evol_aaorop.ps
%python plot_stream.py ../tex/gd1_evol_aaarap.ps
\end{figure}
